Automatic Parallelization and Transparent Fault Tolerance\\ (New project paper)

### 2016-04-06 pubs/tfp16/paper.tex

\begin{itemize}
\item Constructors as functions \\
  (partial application uses generated functions, full creates CONS)

\item Primitive operations as functions \\
  (partial application uses generated functions, full creates EPrimop)

\item Lambda Expressions \\
  (desugar to let-bound FUN objects)

\item Type Annotations \\
  (passed on to type checker)

\item Haskell Block \\
  (ignored by MHS front-end, not other Haskell compilers;
  allows the same file to be tested on our compiler vs GHC)
\end{itemize}

>>>>

mini-Haskell provides some smaller conveniences that don't warrant their own
section, but are worth mentioning.

\begin{itemize}
\item Constructors as functions \\
  As in Haskell, constructors are first class, acting as true functions.  This
  is implemented by simply generating a function that wraps the appropriate
  \texttt{let}-bound \texttt{CON} object in STG.  Any partially applied
  constructor generates a call to this function.  Fully applied constructors
  generate local \texttt{let}-bound objects to avoid an unnecessary function
  call.

\item Primitive operations as functions \\
  Similar to constructors, primitive operations are given first-class status as
  functions, with roughly the same rules.  Partially applied calls are
  translated to generated functions that wrap the actual primitive
  operations. Fully applied calls generate true primitive operation calls.

\item Lambda Expressions \\
  mini-Haskell supports anonymous lambda expressions for the simple, one-off
  functions that often find a place in Haskell code.  This was certainly the
  simplest feature to add, requiring only that the function be given a unique
  identifier to bind it to a \texttt{FUN} object in STG.

\item Type Annotations \\
  The ability to assert the type of some variable is often valuable as a
  sanity-check and provides documentation that the compiler can verify.
  mini-Haskell's type annotations (or signatures) behave like those in
  Haskell, being passed to the typechecker as initial assumptions.

% I don't think I've described this very well at all... - david
\item Haskell Block \\
  Being a subset of Haskell, it may be desireable to test a mini-Haskell program
  compiled through our toolchain against the same program (and same source file)
  compiled with another Haskell compiler.  Because mini-Haskell exposes a
  different set of primitives, the Haskell Block was introduced, to allow the
  inclusion of the \texttt{MagicHash} extension and the aliasing Haskell's
  primitives (e.g. \texttt{(+)} and \texttt{(-)}) to the names given in
  mini-Haskell.  This block, delimited by \texttt{\{-\#-\}} strings, is ignored
  by the mini-Haskell compiler, and arbitrary ``real'' Haskell code can be
  placed therein to create the same mini-Haskell environment for full Haskell
  compilers.

\end{itemize}
